Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-03-04 paper.tex
pequeñas correcciones de ortografia

\item[(b)] We will consider the parameter set from Ref.~\cite{helbing_2000}  as
a starting point for exploring the parameter space. The reason for this is  that
a complete set of experimental parameters is still not available (to our
konwledge). We are aware, though, of the drawbacks of this choice, say, the
unrealistic meanings for the length $B$ and the compressibility $k_n$ (see
Section~\ref{experimental}). But these are irrelevant in the context of the
(dimensionless) parameter space and the corresponding collective dynamics (see
Section~\ref{introduction}).

@@

The regime for $v_d<2\,$m/s is qualitatively different from the clogged regime
since most of the  pedestrians are not touching each other (as was already
observed in Ref~\cite{dorso_2005,dorso_2011}). The only pedestrians who touch
each  other are the ones who are being re-injected on the opposite side of the
room. These collide with the bulk, providing some kind of overlap during very
short time. We will not analize this regime.\\

@@

According to the empirical measurements at Jamaraat, the flow slows down for
high enough densities due to jamming. Notice that the original SFM
(corresponding to $\mathcal{K}=$137) does not produce the expected slowing down
for null body force ($\mathcal{K}_c=$0). However, when the body force is present
(the original SFM) an ``U'' shape behavior occcurs for densities above 5
p$^{-2}$.\\

>>>>

\item[(b)] We will consider the parameter set from Ref.~\cite{helbing_2000}  as
a starting point for exploring the parameter space. The reason for this is  that
a complete set of experimental parameters is still not available (to our
knowledge). We are aware, though, of the drawbacks of this choice, say, the
unrealistic meanings for the length $B$ and the compressibility $k_n$ (see
Section~\ref{experimental}). But these are irrelevant in the context of the
(dimensionless) parameter space and the corresponding collective dynamics (see
Section~\ref{introduction}).

@@

The regime for $v_d<2\,$m/s is qualitatively different from the clogged regime
since most of the  pedestrians are not touching each other (as was already
observed in Ref~\cite{dorso_2005,dorso_2011}). The only pedestrians who touch
each  other are the ones who are being re-injected on the opposite side of the
room. These collide with the bulk, providing some kind of overlap during very
short time. We will not analyze this regime.\\

@@

According to the empirical measurements at Jamaraat, the flow slows down for
high enough densities due to jamming. Notice that the original SFM
(corresponding to $\mathcal{K}=$137) does not produce the expected slowing down
for null body force ($\mathcal{K}_c=$0). However, when the body force is present
(the original SFM) an ``U'' shape behavior occurs for densities above 5
p$^{-2}$.\\
